### 2021-08-04 doc/thesis/chapters/results.tex
remove commented table for detailed LOC
measure matlab sim speed
time logging table

%\begin{GenericCode}
%Matlab:
%  Language     files blank comment code TotalWithoutBlank Total
%  ____________ _____ _____ _______ ____ _________________ _____
%  MATLAB          34   551     728 1451              2179  2730
%
%VHDL IP Design:
%  Language     files blank comment code TotalWithoutBlank Total
%  ____________ _____ _____ _______ ____ _________________ _____
%  VHDL            20   525     787 1431              2218  2743
%  Python           1    45      22  141               163   208
%
%VHDL Testbench:
%  Language     files blank comment code TotalWithoutBlank Total
%  ____________ _____ _____ _______ ____ _________________ _____
%  Python           5   141     141  426               567   708
%  make             2    19      18   70                88   107
%  Bourne Shell     1     5       6   16                22    27
%
%HLS IP Design:
%  Language     files blank comment code TotalWithoutBlank Total
%  ____________ _____ _____ _______ ____ _________________ _____
%  C/C++ Header    14    90     119  221               340   430
%  C++              9    97     197  195               392   489
%
%HLS Testbench:
%  Language     files blank comment code TotalWithoutBlank Total
%  ____________ _____ _____ _______ ____ _________________ _____
%  C++              1    39      44  141               185   224
%  Tcl/Tk           5    33      37  112               149   182
%  C/C++ Header     2    24      18   87               105   129
%  make             1    24      26   69                95   119
%  Python           1    19      21   45                66    85
%\end{GenericCode}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Simulation}
% Sim speed of x min of recorded FM signal
%
% VHDL:
%          time                samples
%   audio         sim        in      out
%  0.1000 s    73:44 min  (96000 -> 4000)
%  0.0100 s    09:37 min  ( 9600 ->  400)
%  0.0025 s    02:36 min  ( 2400 ->  100)
%
% HLS:

@@

%%%%%%%%%%%%%%%%%%%%
\subsection{Integration}
% IP generation and integration into Vivado

%%%%%%%%%%%%%%%%%%%%
\subsection{Hardware Utilization}
% --> utilization reports

>>>>

@@

The metric of implementation time -- the time it takes to implement a specific feature -- is a subjective measure, since it heavily depends on the respective developer's experience, as already noted above.
However, this metric is used in this section to specifically compare HLS with VHDL.
Certain features are chosen for this comparison and their implementation times were logged during the actual implementation process.
Table \ref{tab:implementation_time_logging} shows the direct comparison between HLS and VHDL implementation times.

\begin{table}[]
  \centering
  \begin{tabular}{l|c|c|}
  \cline{2-3}
                                                   & \multicolumn{2}{c|}{\textbf{Time [h]}} \\ \hline
  \multicolumn{1}{|l|}{\textbf{Feature}}           & \textbf{HLS}      & \textbf{VHDL}      \\ \hline
  \multicolumn{1}{|l|}{AXI Stream Interface}       & 8                 & 12                 \\ \hline
  \multicolumn{1}{|l|}{AXI4-Lite Interface}        & 2                 & 10                 \\ \hline
  \multicolumn{1}{|l|}{LED Control Register}       & 1                 & 2                  \\ \hline
  \multicolumn{1}{|l|}{Build Information Register} & 8                 & 5                  \\ \hline
  \multicolumn{1}{|l|}{Pass-Through Mode Register} & 1                 & 1                  \\ \hline
  \multicolumn{1}{|l|}{FIR Filter}                 & 13                & 7                  \\ \hline
  \multicolumn{1}{|l|}{Sample Decimation}          & 15                & 1                  \\ \hline
  \multicolumn{1}{|l|}{Receiver Structure}         & 13                & 33                 \\ \hline
  \multicolumn{1}{|l|}{\textbf{Sum}}               & \textbf{61}       & \textbf{71}        \\ \hline
  \end{tabular}
  \caption{Implementation time logging for a specific set of features, for the direct comparison between HLS and VHDL.}
  \label{tab:implementation_time_logging}
\end{table}

@@

% Issues
% -- HLS Debug Error with Bitwidth:
%       Not sure what the error was.
%       Parallel delay for I/Q didn't work.
%       The order of every 2nd data value was wrong.
%       Using a single delay fixed it.
% -- HLS driver generation
%       Fixing issue with auto-generated driver.
%       It did not get imported into the SDK.
%       Problem was that HLS project and top-level
%       did not have the same name....

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Simulation}

Sim speed of x min of recorded FM signal\\
bla bla
%
% VHDL:
%          time                samples
%   audio         sim        in      out
%  0.1000 s    73:44 min  (96000 -> 4000)
%  0.0100 s    09:37 min  ( 9600 ->  400)
%  0.0025 s    02:36 min  ( 2400 ->  100)
%
% HLS:
%
%
% Matlab:
%          time                samples
%   audio         sim        in      out
%  1.7 s    0.45 sec     1632000   68000
%

@@

%%%%%%%%%%%%%%%%%%%%
\subsection{Integration}
% IP generation and integration into Vivado
% Issue: HLS driver import did not work - Vivado SDK is a mess (bad UI based on Eclipse, has bugs, no error output, etc...)
%%%%%%%%%%%%%%%%%%%%
\subsection{Hardware Utilization}
% --> utilization reports
